COG-ED Manuscript

### 2021-12-02 06_Paper/COG-ED/Manuscript.Rmd
corrected exclusion of 100ms trials

    # exclude RTs fast than 100 ms after stimulus onset if the fourth letter in the data frame name is a "T"

@@

      pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]

>>>>

    # exclude RTs fast than 100 ms after stimulus onset if the fourth letter in the data frame name is a "T"
    # also making sure that there are even any trials below 100 ms, otherwise you get an error message

@@

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ],
             pipelines_data[[i]] <- pipelines_data[[i]])
    }
